Fundamentals of Computing and Data Display

### 2022-12-05 paper-template.Rmd
changes Carlos

---
title: "Fundamentals of Computing and Data Display"
subtitle: "Term paper template"
author: "Tim Raxworthy & Carlos Cristiano"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes
    df_print: kable
references:
- id: Marshall2016
  title: Why conserve primates? In An Introduction to Primate Conservation
  author:
  - family: Marshall
    given: Andrew J.
  - family: Wich
    given: Serge A.
  page: 13-29
  type: book
  container-title: Oxford Academic
  issued:
    year: 2016

  - id: Estrada2017
  title: Impending extinction crisis of the world’s primates`:` Why primates matter
  author:
  - family: Estrada
    given: Alejandro
  - family: et al.
  container-title: Science Advances
  issued:
    year: 2017
---

```{r, include = FALSE}
library(knitr)
library(tidyverse)
```

@@

```{r}
# A code chunk that exemplifies the data gathering process
```

```{r, include = FALSE}
# Additional code chunks that repeat tasks or do basic things can be hidden
```

@@

>>>>

---
title: "Fundamentals of Computing and Data Display"
subtitle: "Term paper template"
author: "Tim Raxworthy & Carlos Cristiano"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes
    df_print: kable
references:
- id: Wickham2014
  title: Tidy Data
  author:
  - family: Wickham
    given: Hadley
  container-title: Journal of Statistical Software
  volume: 59
  issue: 10
  page: 1-23
  type: article-journal
  issued:
    year: 2014
- id: Baumer2017
  title: Modern Data Science with R
  author:
  - family: Baumer
    given: Benjamin S.
  - family: Kaplan
    given: Daniel T.
  - family: Horton
    given: Nicholas J.
  type: book
  publisher: Chapman \& Hall/CRC Press.
  issued:
    year: 2017
---

```{r, include = FALSE}
library(knitr)
library(tidyverse)
library(quanteda)
library(topicmodels)
library(tidyverse)
library(tm)
library(SnowballC)
library(wordcloud)
library(rtweet)
library(reshape2)
library(ggplot2)
library(textmineR)
library(ggwordcloud)
```

@@

```{r}
Data.science <- search_tweets(
  q = "monkey", # search for Tweets with "data" AND "science",
  n = 4000 
)
data = Data.science %>%
  select(full_text) %>%
  mutate(doc_id=seq(n())) %>%
  data.frame()

corpus_sotu_orig <- corpus(data, 
                           docid_field = "doc_id",
                           text_field = "full_text")

corpus_sotu_proc <- tokens(corpus_sotu_orig, 
                           remove_punct = TRUE, # remove punctuation
                           remove_numbers = TRUE, # remove numbers
                           remove_symbols = TRUE) %>% 
  tokens_tolower() 
lemmaData <- read.csv2("baseform_en.tsv",
                       sep="\t", 
                       header=FALSE, 
                       encoding = "UTF-8", 
                       stringsAsFactors = F)

lemmaData = lemmaData %>% 
  filter(!is.na(V1))
cloud =lemmaData %>% 
  group_by(V2) %>% 
  mutate(freq=n()) %>% 
  distinct(freq,V2) %>% 
  filter(freq<40) %>% 
  arrange(desc(freq))

cloud = cloud[1:100,]

wordcloud(words = cloud$V2, freq = cloud$freq, min.freq = 1,
          max.words=200, random.order=TRUE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

@@

```{r}
corpus_sotu_proc <-  tokens_replace(corpus_sotu_proc, 
                                    lemmaData$V1, 
                                    lemmaData$V2,
                                    valuetype = "fixed")

corpus_sotu_proc <- corpus_sotu_proc %>%
  tokens_remove(stopwords("english")) %>%
  tokens_ngrams(1)
DTM <- dfm(corpus_sotu_proc)
minimumFrequency <- 10
DTM <- dfm_trim(DTM, 
                min_docfreq = minimumFrequency,
                max_docfreq = 100)
DTM  <- dfm_select(DTM, 
                   pattern = "[a-z]", 
                   valuetype = "regex", 
                   selection = 'keep')
colnames(DTM) <- stringi::stri_replace_all_regex(colnames(DTM), 
                                                 "[^_a-z]","")

DTM <- dfm_compress(DTM, "features")
sel_idx <- rowSums(DTM) > 0
DTM <- DTM[sel_idx, ]
textdata <- data[sel_idx, ]

model <- FitLdaModel(dtm = DTM,
                     k = 20,
                     iterations = 200, # I usually recommend at least 500 iterations or more
                     burnin = 180,
                     alpha = 0.1,
                     beta = 0.05,
                     optimize_alpha = TRUE,
                     calc_likelihood = TRUE,
                     calc_coherence = TRUE,
                     calc_r2 = TRUE,
                     cpus = 2)
model2=as.data.frame(model$log_likelihood)
ggplot(model2,aes(x=iteration,y=log_likelihood))+
  geom_line()+
  geom_vline(xintercept = 10, col="red")+
  labs(title = "k = 10")

K <- 10

topicModel <- LDA(DTM, 
                  K, 
                  method="Gibbs", 
                  control=list(iter = 500, 
                               verbose = 25))
tmResult <- modeltools::posterior(topicModel)
beta <- tmResult$terms

theta <- tmResult$topics

#terms(topicModel, 10)
top5termsPerTopic <- terms(topicModel, 
                           5)
# For the next steps, we want to give the topics more descriptive names 
#than just numbers. Therefore, we simply concatenate the five most likely
#terms of each topic to a string that represents a pseudo-name for each topic.
topicNames <- apply(top5termsPerTopic, 
                    2, 
                    paste, 
                    collapse=" ")
topicProportions <- colSums(theta) / nrow(DTM)  # average probability over all paragraphs
names(topicProportions) <- topicNames     # Topic Names
sort(topicProportions, decreasing = TRUE)
attr(topicModel, "alpha") 
topicModel2 <- LDA(DTM, 
                   K, 
                   method="Gibbs", 
                   control=list(iter = 500, 
                                verbose = 25, 
                                alpha = 0.2))#replace alpha

tmResult <- modeltools::posterior(topicModel2)
theta <- tmResult$topics
beta <- tmResult$terms

topicProportions <- colSums(theta) / nrow(DTM)  # average probability over all paragraphs
names(topicProportions) <- topicNames     # Topic Names 
sort(topicProportions, decreasing = TRUE) 
topicNames <- apply(terms(topicModel2, 5), 2, paste, collapse = " ")
exampleIds <- c(2, 100, 200)
N <- length(exampleIds)

topicProportionExamples <- as.tibble(theta) %>%
  slice(exampleIds)

colnames(topicProportionExamples) <- topicNames

vizDataFrame <- melt(cbind(data.frame(topicProportionExamples), 
                           document = factor(1:N)), 
                     variable.name = "topic", 
                     id.vars = "document")

ggplot(data = vizDataFrame, 
       aes(topic, value, 
           fill = document), 
       ylab = "proportion") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1)) +  
  coord_flip() +
  facet_wrap(~ document, 
             ncol = N)

```
